
\subsubsection{Evaluator 1 user testing scores}

\subsubsection*{User testing record tables}
The following is a list of tables representing the most relevant quantitative and qualitative data collected during the user testing practice by the first evaluator.
Along with each table there is a section dedicated to comments and observations that the inspector managed to collect while running the tests on the user.

\vspace{0.8cm}

{
	\centering
	\renewcommand{\arraystretch}{1.2}
	\begin{minipage}{\textwidth}
		
		\centering	{ \large \textbf{User n°1}}
		\vspace{0.3cm}
		
		\begin{tabularx}{\textwidth}{|*{4}{>{\centering\arraybackslash}X|} >{\centering\arraybackslash}p{2.2cm}| >{\centering\arraybackslash}p{2.2cm}|}
			\hline
			\nohyphens{\textbf{Task Number}}& \textbf{Start Time} & \textbf{End Time} & \textbf{Elapsed time} & \nohyphens{ \textbf{Task Completion}} & \textbf{Task difficulty} \\ \hline
			1 & 10:23 & 10:28 & 4:40 & Completed ASSISTED & 4 \\ \hline
			2 & 10:29 & 10:32 & 1:41 & Completed & 2 \\ \hline
			3 & 10:32 & 10:33 & 1:03 & Completed ALT & 2 \\ \hline
			4 & 10:34 & 10:35 & 1:12 & Completed & 3 \\ \hline
			5 & 10:36 & 10:37 & 0:55 & Completed & 1 \\ \hline
			6 & 10:37 & 10:39 & 1:55 & Completed ALT & 2 \\ \hline
		\end{tabularx}
		
		\vspace{0.7cm}
	\end{minipage}
}
\noindent
{\large \textbf{Comments and observations}}
% Space for comments here
\begin{itemize}
    \item \textbf{Task 1:} Initially, she was confused by the unfamiliar structure of the website and needed assistance to locate the gender page. Once she found it, she easily accessed the resources. She encountered no issues with the other pages but was perplexed by the differences.
    \item \textbf{Task 2:} She initially entered the general donation section. After a while, she searched for Afghanistan and quickly found the dedicated website. Once there, she easily located the donation section.
    \item \textbf{Task 3:} She initially experienced difficulties navigating back to the home page. However, she utilized the "Where We Work" link from the footer. From there, she quickly understood how to locate the Italian website.
    \item \textbf{Task 4:} She followed the correct path to find the report but experienced some confusion with the solutions section. Initially, she focused solely on the first solution.
    \item \textbf{Task 5:} She immediately located the job search page and then easily utilized the filters.
    \item \textbf{Task 6:} She encountered difficulties returning to the correct website initially, but eventually managed to find the article using a different path.
\end{itemize}





\vspace{1cm}

{
	\centering
	\renewcommand{\arraystretch}{1.2}
	\begin{minipage}{\textwidth}
		
		\centering	{ \large \textbf{User n°2}}
		\vspace{0.3cm}
		
		\begin{tabularx}{\textwidth}{|*{4}{>{\centering\arraybackslash}X|} >{\centering\arraybackslash}p{2.2cm}| >{\centering\arraybackslash}p{2.2cm}|}
			\hline
			\nohyphens{\textbf{Task Number}}& \textbf{Start Time} & \textbf{End Time} & \textbf{Elapsed time} & \nohyphens{ \textbf{Task Completion}} & \textbf{Task difficulty} \\ \hline
			1 & 14:57 & 15:05 & 7:41 & Completed & 5 \\ \hline
			2 & 15:06 & 15:11 & 5:15 & Completed & 4 \\ \hline
			3 & 15:13 & 15:13 & 0:20 & Completed & 1 \\ \hline
			4 & 15:14 & 15:19 & 4:18 & Completed & 4 \\ \hline
			5 & 15:20 & 15:25 & 4:55 & Completed ASSISTED & 5 \\ \hline
			6 & 15:26 & 15:27 & 1:34 & Completed & 1 \\ \hline
		\end{tabularx}
		
		\vspace{0.7cm}
	\end{minipage}
}
\noindent
{\large \textbf{Comments and observations}}
% Space for comments here
\begin{itemize}
    \item \textbf{Task 1:} She quickly located the page but faced difficulties in finding the resources, as well as with the other pages. She took a lot of time.
    \item \textbf{Task 2:} She initially entered the general donation page but encountered confusion when attempting to navigate to another page due to menu options. It took her a considerable amount of time to locate the Afghanistan page, causing some stress during the search. However, she managed to find the donation section.
    \item \textbf{Task 3:} She completed the task without encountering any problems, completing it immediately.
    \item \textbf{Task 4:} She had to resort to using the browser's back arrow. While she easily found the report, she encountered difficulties in understanding the solutions provided within it. There was a lot of confusion within the report itself.
    \item \textbf{Task 5:} She initially attempted to use the search bar but without success. Initially, she struggled to determine what to search for, but with some assistance, she managed to find the page. However, she encountered a bit of difficulty with the filters due to the abundance of options available.
    \item \textbf{Task 6:} She completed the task smoothly and accurately without encountering any problems.
\end{itemize}





\vspace{1cm}

{
	\centering
	\renewcommand{\arraystretch}{1.2}
	\begin{minipage}{\textwidth}
		
		\centering	{ \large \textbf{User n°3}}
		\vspace{0.3cm}
		
		\begin{tabularx}{\textwidth}{|*{4}{>{\centering\arraybackslash}X|} >{\centering\arraybackslash}p{2.2cm}| >{\centering\arraybackslash}p{2.2cm}|}
			\hline
			\nohyphens{\textbf{Task Number}}& \textbf{Start Time} & \textbf{End Time} & \textbf{Elapsed time} & \nohyphens{ \textbf{Task Completion}} & \textbf{Task difficulty} \\ \hline
			1 & 14:00 & / & / & Failure & 5 \\ \hline
			2 & 14:06 & 14:07 & 0:30 & Completed & 1 \\ \hline
			3 & 14:08 & 14:10 & 1:56 & Completed & 3 \\ \hline
			4 & 14:11 & 14:15 & 4:04 & Completed ALT & 3 \\ \hline
			5 & 14:18 & 14:21 & 2:59 & Completed ALT & 2 \\ \hline
			6 & 14:22 & 14:23 & 1:06 & Completed & 1 \\ \hline
		\end{tabularx}
		
		\vspace{0.7cm}
	\end{minipage}
}
\noindent
{\large \textbf{Comments and observations}}
% Space for comments here
\begin{itemize}
    \item \textbf{Task 1:} She initially attempted to use the search bar but couldn't locate the right page. Then, she became confused with the menus until finally finding the correct page. However, once on the right page, she struggled to find the resources button, which was less visible. Unfortunately, she couldn't complete the task, leading to accumulated stress.
    \item \textbf{Task 2:} She directly searched for the Afghanistan page and found it immediately. Similarly, she had no trouble finding the donation section.
    \item \textbf{Task 3:} She had to use the website's back arrow to navigate, then found the right page with some difficulty. It took her a bit of time to locate the Italian website.
    \item \textbf{Task 4:} She immediately found the correct article using the search bar and then used the accelerator to navigate to the solutions section. However, she encountered confusion in understanding which solutions were presented.
    \item \textbf{Task 5:} Initially, she attempted to use the search bar without success. Then, she experienced confusion with the menus again until she eventually reached the correct page through a longer path. Once on the page, she had no problem using the filters.
    \item \textbf{Task 6:} She easily found the page and then the article without encountering any difficulties.
\end{itemize}







\vspace{1cm}

{
	\centering
	\renewcommand{\arraystretch}{1.2}
	\begin{minipage}{\textwidth}
		
		\centering	{ \large \textbf{User n°4}}
		\vspace{0.3cm}
		
		\begin{tabularx}{\textwidth}{|*{4}{>{\centering\arraybackslash}X|} >{\centering\arraybackslash}p{2.2cm}| >{\centering\arraybackslash}p{2.2cm}|}
			\hline
			\nohyphens{\textbf{Task Number}}& \textbf{Start Time} & \textbf{End Time} & \textbf{Elapsed time} & \nohyphens{ \textbf{Task Completion}} & \textbf{Task difficulty} \\ \hline
			1 & 12:15 & 12:20 & 4:32 & Completed & 4 \\ \hline
			2 & 12:21 & 12:24 & 3:13 & Completed & 3 \\ \hline
			3 & 12:26 & 12:34 & 7:28 & Completed ASSISTED & 5 \\ \hline
			4 & 12:35 & 12:41 & 6:02 & Completed & 5 \\ \hline
			5 & 12:43 & 12:47 & 3:26 & Completed ALT & 4 \\ \hline
			6 & 12:48 & 12:52 & 3:50 & Completed & 2 \\ \hline
		\end{tabularx}
		
		\vspace{0.7cm}
	\end{minipage}
}
\noindent
{\large \textbf{Comments and observations}}
% Space for comments here
\begin{itemize}
    \item \textbf{Task 1:} She was completely disoriented by the website's organization and couldn't locate the gender page at first. Once she found it, she easily located the resources as well. There were no issues with the other pages, but she inquired about why they were different.
    \item \textbf{Task 2:} She initially entered the general donation page. After a while, she decided to change pages and searched for Afghanistan. Eventually, she quickly found the donation section. Throughout this process, she expressed frustration with the site.
    \item \textbf{Task 3:} Initially, she tried the search bar without any success, struggling to determine where to search and requiring assistance. Even with the help provided, she took a lot of time to complete the task.
    \item \textbf{Task 4:} She encountered difficulties navigating back to the website and had trouble finding the report. At one point, the website completely froze, causing considerable stress.
    \item \textbf{Task 5:} She quickly found the page but realized it seemed incorrect, prompting her to change course. Upon revisiting the page through a different path, she successfully completed the task. While the filters were easy to use, she felt confused about the rest of the process.
    \item \textbf{Task 6:} She struggled to navigate back to the website and experienced confusion and stress while trying to find the right page.
\end{itemize}




\vspace{1cm}

{
	\centering
	\renewcommand{\arraystretch}{1.2}
	\begin{minipage}{\textwidth}
		
		\centering	{ \large \textbf{User n°5}}
		\vspace{0.3cm}
		
		\begin{tabularx}{\textwidth}{|*{4}{>{\centering\arraybackslash}X|} >{\centering\arraybackslash}p{2.2cm}| >{\centering\arraybackslash}p{2.2cm}|}
			\hline
			\nohyphens{\textbf{Task Number}}& \textbf{Start Time} & \textbf{End Time} & \textbf{Elapsed time} & \nohyphens{ \textbf{Task Completion}} & \textbf{Task difficulty} \\ \hline
			1 & 16:32 & 16:40 & 7:48 & Completed ASSISTED & 5 \\ \hline
			2 & 16:42 & 16:44 & 2:30 & Completed & 2 \\ \hline
			3 & 16:45 & 16:49 & 3:33 & Completed & 4 \\ \hline
			4 & 16:51 & 16:54 & 3:07 & Completed & 2 \\ \hline
			5 & 16:55 & 16:59 & 3:54 & Completed ALT & 3 \\ \hline
			6 & 17:01 & 17:04 & 2:39 & Completed & 3 \\ \hline
		\end{tabularx}
		
		\vspace{0.7cm}
	\end{minipage}
}
\noindent
{\large \textbf{Comments and observations}}
% Space for comments here
\begin{itemize}
    \item \textbf{Task 1:} She quickly located the "gender" page but encountered difficulties in finding the "Resources" button, feeling confused during the search within the page. Additionally, she was confused by the differences in the other pages, which she found after a lot of time with assistance.
    \item \textbf{Task 2:} Initially, she clicked on the donate button at the top of the website, but it wasn't immediately clear that it wasn't the correct page. Then, she attempted to search for the keyword "Afghanistan" and eventually found the right page. There was a sense of nervousness during the search process.
    \item \textbf{Task 3:} She remained nervous during the search for the page because it was not clear, even after entering the correct page. She couldn't immediately find the Italian section. The page was very confusing overall.
    \item \textbf{Task 4:} She easily found the report and then navigated to the "Solutions" section using accelerators. Initially, she focused on the first solution, but after a while, she scrolled to the others. However, it wasn't clear where the other solutions were located.
    \item \textbf{Task 5:} She arrived at the job search after visiting some other pages. Once she found this section, it was easy for her to search for the right job.
    \item \textbf{Task 6:} Initially, she had to use the back arrow of the browser to reach the correct website. She immediately found the COVID-19 topic but felt very confused due to the large number of articles. After a while, she managed to find the right article but felt nervous during the process.
\end{itemize}


\clearpage




\subsubsection*{Post-test questionnaire results}
This section is dedicated to a summary table that helps illustrating how the users responded to the post-test questionnaire they've been required to fill in.\\

{
	\renewcommand{\arraystretch}{1.2}
	\centering
	\begin{tabularx}{\textwidth}{|*{6}{>{\centering\arraybackslash}X|}}
		\hline
		\multirow{2}{*}{\textbf{Question}} & \multicolumn{5}{c|}{\textbf{Participant ID}} \\ \cline{2-6}
		& 1 & 2 & 3 & 4 & 5 \\ \hline
		1 & N & D & D & N & D \\ \hline
		2 & A & D & N & SD & N \\ \hline
		3 & A & D & A & SD & N \\ \hline
		4 & SA & SA & N & SA & A \\ \hline
		5 & A & N & A & N & A \\ \hline
		6 & D & A & SA & A & A \\ \hline
		7 & N & D & N & A & SA \\ \hline
		8 & A & D & SA & N & N \\ \hline
		9 & D & A & D & SD & A \\ \hline
		10 & N & SD & D & D & A \\ \hline
		11 & N & SA & N & D & N \\ \hline
		12 & A & A & A & SA & SD \\ \hline
		13 & D & SD & D & SD & D \\ \hline
		14 & D & D & N & N & D \\ \hline
		15 & A & A & SA & A & A \\ \hline
		16 & D & SD & SD & A & D \\ \hline
		17 & SA & SA & A & D & A \\ \hline
		18 & SA & SA & A & SD & A \\ \hline
	\end{tabularx}
}


\textbf{Legend:} SA = Strongly Agree, A = Agree, N = Neutral, D = Disagree, SD = Strongly Disagree

\vspace{0.5cm}

\textbf{Adjectives per participant:}
\begin{enumerate}
	\item Useful, Dispersive, Counterintuitive
	\item Complicated, Consistent, Slow
	\item Messy, Counterintuitive, Consistent
	\item Unclear, Complex, Aesthetically Pleasing
	\item Messy, Unaesthetic, Less Engaging
\end{enumerate}

\vspace{0.25cm}

\textbf{Additional comments per participant:}
\begin{enumerate}
	\item /
	\item /
	\item /
	\item The whole thing needs to be reviewed thoroughly because it's not up to par. It needs to standardize the colors, and the donation button should provide access to all possible donations. Unnecessary buttons should be removed, and the search button should be a functional element, not just a decorative feature because it's not working!
	\item /
\end{enumerate}