\subsubsection{Evaluator 3 user testing scores}

\subsubsection*{User testing record tables}
The following is a list of tables representing the most relevant quantitative and qualitative data collected during the user testing practice by the third evaluator.
Along with each table there is a section dedicated to comments and observations that the inspector managed to collect while running the tests on the user.

\vspace{0.8cm}

{
	\centering
	\renewcommand{\arraystretch}{1.2}
	\begin{minipage}{\textwidth}
		
		\centering	{ \large \textbf{User n°1}}
		\vspace{0.3cm}
		
		\begin{tabularx}{\textwidth}{|*{4}{>{\centering\arraybackslash}X|} >{\centering\arraybackslash}p{2.2cm}| >{\centering\arraybackslash}p{2.2cm}|}
			\hline
			\nohyphens{\textbf{Task Number}}& \textbf{Start Time} & \textbf{End Time} & \textbf{Elapsed time} & \nohyphens{ \textbf{Task Completion}} & \textbf{Task difficulty} \\ \hline
			1 & 19:06 & 19:14 & 8:07 & Partial & 5 \\ \hline
			2 & 19:14 & 19:22 & 8:26 & Completed ALT & 4 \\ \hline
			3 & 19:23 & 19:25 & 2:41 & Completed ALT & 1 \\ \hline
			4 & 19:26 & 19:29 & 3:27 & Completed ALT & 2 \\ \hline
			5 & 19:30 & 19:32 & 2:10 & Completed & 2 \\ \hline
			6 & 19:32 & 19:35 & 3:44 & Completed ALT & 2 \\ \hline
		\end{tabularx}
		
		\vspace{0.7cm}
	\end{minipage}
}
\noindent
{\large \textbf{Comments and observations}}
\begin{enumerate}
	\item Before tackling the actual first task, the participant looked and explored a bit the website on their own. The participant only found the solution for "Nutrition", but in a alternative way: from the home page click on the "Child survival" icon and click on the link "Nutrition", from there the user found the correct answer. For the other two cases the user interacted with the icons off the same section, but did not understand the meaning of the subsequent links and did not even click them.
	\item Firstly the user tried to donate (normal). To do so they went on the "Take Action" sub-menu and from there went to the donate page by clicking on "Donate".\\
	To properly accomplish the task the user used the search feature searching for "Afghanistan", then they scrolled down and went to the page: \href{https://www.unicef.org/appeals/afghanistan}{UNICEF Afghanistan Appeal} where they clicked on the button "Donate now", reaching the end.
	\item The user, firstly, looked for "Italy" in the stories section, since they did not find it, the user searched for the same keyword in the search feature. From there they scrolled down until a link to the Page (of 16 Jan 2018) titled Italy.
	\item The user directly searched for "The State of the World's Children 2023" in the search feature (no suggestions from the system). From there they found the report and scrolled down finding the 4 solutions.
	\item -
	\item The user searched for "Covid-19 vaccination Bangladesh" via the search feature and from there found the first article.
\end{enumerate}

\vspace{1cm}

{
	\centering
	\renewcommand{\arraystretch}{1.2}
	\begin{minipage}{\textwidth}
		
		\centering	{ \large \textbf{User n°2}}
		\vspace{0.3cm}
		
		\begin{tabularx}{\textwidth}{|*{4}{>{\centering\arraybackslash}X|} >{\centering\arraybackslash}p{2.2cm}| >{\centering\arraybackslash}p{2.2cm}|}
			\hline
			\nohyphens{\textbf{Task Number}}& \textbf{Start Time} & \textbf{End Time} & \textbf{Elapsed time} & \nohyphens{ \textbf{Task Completion}} & \textbf{Task difficulty} \\ \hline
			1 & 17:22 & 17:34 & 12:03 & Completed ASSISTED & 5 \\ \hline
			2 & 17:34 & 17:36 & 2:32 & Completed & 2 \\ \hline
			3 & 17:37 & 17:39 & 2:06 & Completed & 1 \\ \hline
			4 & 17:39 & 17:45 & 6:16 & Completed ASSISTED & 3 \\ \hline
			5 & 17:46 & 17:50 & 4:15 & Completed & 2 \\ \hline
			6 & 17:50 & 17:58 & 8:55 & Failure & 5 \\ \hline
		\end{tabularx}
		
		\vspace{0.7cm}
	\end{minipage}
}
\noindent
{\large \textbf{Comments and observations}}
\begin{enumerate}
	\item The user, after exploring the site, found the correct pages in the "What We Do" section, but they needed some time and confirmation to find the correct resources in their different formats.
	\item -
	\item -
	\item The user was unsure of the correct solutions and needed confirmation.
	\item -
	\item The user could not find the proper target page. They searched in all subsections unsuccessfully. They particularly focused on the "Stories" section, trying to find in vain a sub-section dedicated to "Bangladesh". In the "What We Do" section, the user overlooked the sub-section "COVID-19 response" and focused on the "Immunization" one.
\end{enumerate}

\vspace{1cm}

{
	\centering
	\renewcommand{\arraystretch}{1.2}
	\begin{minipage}{\textwidth}
		
		\centering	{ \large \textbf{User n°3}}
		\vspace{0.3cm}
		
		\begin{tabularx}{\textwidth}{|*{4}{>{\centering\arraybackslash}X|} >{\centering\arraybackslash}p{2.2cm}| >{\centering\arraybackslash}p{2.2cm}|}
			\hline
			\nohyphens{\textbf{Task Number}}& \textbf{Start Time} & \textbf{End Time} & \textbf{Elapsed time} & \nohyphens{ \textbf{Task Completion}} & \textbf{Task difficulty} \\ \hline
			1 & 21:03 & 21:08 & 5:39 & Completed & 3 \\ \hline
			2 & 21:09 & 21:19 & 10:35 & Completed ALT & 5 \\ \hline
			3 & 21:20 & 21:22 & 2:11 & Completed & 1 \\ \hline
			4 & 21:22 & 21:25 & 3:25 & Completed & 1 \\ \hline
			5 & 21:26 & 21:30 & 4:42 & Completed ALT & 2 \\ \hline
			6 & 21:31 & 21:35 & 4:38 & Completed & 2 \\ \hline
		\end{tabularx}
		
		\vspace{0.7cm}
	\end{minipage}
}
\noindent
{\large \textbf{Comments and observations}}
\begin{enumerate}
	\item -
	\item Firstly the user tried to donate (normal). To do so the participant simply clicked on the main "Donate" button.\\
	To properly accomplish the task the user tried to explore the different sections unsuccessfully. Afterwards, they used the search feature searching for "Afghanistan", then they scrolled down and, after some erroneous pages, went to the page: \href{https://www.unicef.org/appeals/afghanistan}{UNICEF Afghanistan Appeal} where they clicked on the button "Donate now", reaching the end.
	\item -
	\item -
	\item The user reached the correct page via the "Work with us" link in the "About us" sub-section of the "About UNICEF" section.
	\item The user, before completing the task, went on the "Immunization" sub-section of the "What we do" section.
\end{enumerate}

\vspace{1cm}

\clearpage 

{
	\centering
	\renewcommand{\arraystretch}{1.2}
	\begin{minipage}{\textwidth}
		
		\centering	{ \large \textbf{User n°4}}
		\vspace{0.3cm}
		
		\begin{tabularx}{\textwidth}{|*{4}{>{\centering\arraybackslash}X|} >{\centering\arraybackslash}p{2.2cm}| >{\centering\arraybackslash}p{2.2cm}|}
			\hline
			\nohyphens{\textbf{Task Number}}& \textbf{Start Time} & \textbf{End Time} & \textbf{Elapsed time} & \nohyphens{ \textbf{Task Completion}} & \textbf{Task difficulty} \\ \hline
			1 & 18:27 & 18:33 & 6:45 & Completed ALT & 3 \\ \hline
			2 & 18:34 & 18:42 & 8:54 & Completed & 3 \\ \hline
			3 & 18:43 & 18:45 & 2:31 & Completed & 1 \\ \hline
			4 & 18:46 & 18:50 & 4:07 & Completed & 1 \\ \hline
			5 & 18:50 & 18:54 & 4:30 & Completed ALT & 2 \\ \hline
			6 & 18:55 & 19:01 & 6:08 & Completed & 2 \\ \hline
		\end{tabularx}
		
		\vspace{0.7cm}
	\end{minipage}
}
\noindent
{\large \textbf{Comments and observations}}
\begin{enumerate}
	\item The user completed the task, but for the first visited page "Gender Equality" they arrived there via the icon in the home page. Then to go to the second page, the user went back utilizing the undo function of the browser, but stopped to use the section drop-down, when accidentally seeing the possible answer link. For the final page the user used the expected path.
	\item The user spent a lot of time searching where to go, visiting uncorrelated pages (various pages in the "What we do" section), before reaching the correct page.
	\item -
	\item -
	\item The user reached the correct page via the "Work with us" link in the "About us" sub-section of the "About UNICEF" section.
	\item The user, before completing the task, thought that there could have been a dedicated sub-section in the "Stories" section.
\end{enumerate}

\vspace{1cm}

\clearpage 

{
	\centering
	\renewcommand{\arraystretch}{1.2}
	\begin{minipage}{\textwidth}
		
		\centering	{ \large \textbf{User n°5}}
		\vspace{0.3cm}
		
		\begin{tabularx}{\textwidth}{|*{4}{>{\centering\arraybackslash}X|} >{\centering\arraybackslash}p{2.2cm}| >{\centering\arraybackslash}p{2.2cm}|}
			\hline
			\nohyphens{\textbf{Task Number}}& \textbf{Start Time} & \textbf{End Time} & \textbf{Elapsed time} & \nohyphens{ \textbf{Task Completion}} & \textbf{Task difficulty} \\ \hline
			1 & 21:12 & 21:22 & 10:01 & Completed ASSISTED & 4 \\ \hline
			2 & 21:22 & 21:24 & 2:22 & Completed & 1 \\ \hline
			3 & 21:25 & 21:33 & 8:10 & Failure & 5 \\ \hline
			4 & 21:33 & 21:36 & 3:04 & Completed & 2 \\ \hline
			5 & 21:36 & 21:39 & 3:38 & Completed & 1 \\ \hline
			6 & 21:40 & 21:42 & 2:41 & Completed & 1 \\ \hline
		\end{tabularx}
		
		\vspace{0.7cm}
	\end{minipage}
}
\noindent
{\large \textbf{Comments and observations}}
\begin{enumerate}
	\item The user, after exploring the site, found the correct pages in the "What We Do" section, but they needed some time and confirmation to find the correct resources in their different formats.
	\item -
	\item The user could not find the proper target page. They searched in all subsections unsuccessfully. In the About UNICEF section clicked on "Europe and Central Asia" which brought them into the correct page, but presented them a selection (Countries in this region) where there was not Italy.
	\item -
	\item -
	\item -
\end{enumerate}

\clearpage


\subsubsection*{Post-test questionnaire results}
This section is dedicated to a summary table that helps illustrating how the users responded to the post-test questionnaire they've been required to fill in.\\

{
	\renewcommand{\arraystretch}{1.2}
	\centering
	\begin{tabularx}{\textwidth}{|*{6}{>{\centering\arraybackslash}X|}}
		\hline
		\multirow{2}{*}{\textbf{Question}} & \multicolumn{5}{c|}{\textbf{Participant ID}} \\ \cline{2-6}
		& 1 & 2 & 3 & 4 & 5 \\ \hline
		1 & D & D & N & N & D \\ \hline
		2 & D & N & D & D & D \\ \hline
		3 & D & N & D & N & D \\ \hline
		4 & A & N & A & A & SA \\ \hline
		5 & A & N & A & A & A \\ \hline
		6 & A & A & SA & A & A \\ \hline
		7 & A & A & SA & SA & SA \\ \hline
		8 & A & N & SA & A & A \\ \hline
		9 & N & N & D & N & D \\ \hline
		10 & A & N & A & A & D \\ \hline
		11 & D & N & A & D & D \\ \hline
		12 & SA & A & A & SA & N \\ \hline
		13 & D & N & D & D & SD \\ \hline
		14 & N & N & D & D & D \\ \hline
		15 & A & A & N & A & N \\ \hline
		16 & D & D & D & D & N \\ \hline
		17 & SA & A & A & A & SA \\ \hline
		18 & A & A & N & A & N \\ \hline
	\end{tabularx}
}

\textbf{Legend:} SA = Strongly Agree, A = Agree, N = Neutral, D = Disagree, SD = Strongly Disagree

\vspace{0.5cm}

\textbf{Adjectives per participant:}
\begin{enumerate}
	\item Good, Improvable, Visually striking
	\item Positive, Wholesome, Not sad
	\item Cumbersome, Informative, Positive
	\item Helpful, Improvable, For a good cause
	\item Oversaturated, Boring, Clunky
\end{enumerate}

\vspace{0.25cm}

\textbf{Additional comments per participant:}
\begin{enumerate}
	\item Photos are really good and impactful.
	\item It seems like they are actually helping people, showing their appreciation through the website.
	\item The website is ok, nothing incredible, but provides a lot of information about important and difficult topics. It gives an easy way to donate and help those in needs.
	\item When using the website there are some problems: the misleading click on the drop-down menu and the fact that there was too much scrolling to do on pages, making it difficult to navigate and understand your position inside them.
	\item The website is huge, not properly organized and at times frustrating.
\end{enumerate}